An asymptotically normal out-of-sample test based on mixed estimation windows

### 2017-05-15 S2-normality.tex
Split main LaTeX file into several smaller files

\documentclass[12pt,fleqn]{article}
\input{tex/setup}
\input{tex/mcDef}
\input{tex/ap}

% These commands are generated when the Monte Carlo and applied
% sections are run; I'm giving them definitions now so that LaTeX will
% compile the document even if that code hasn't been run yet.
\providecommand\bootsize{[missing]}
\providecommand\empiricalcriticalvalue{[missing]}
\providecommand\nboot{[missing]}
\providecommand\nmod{[missing]}
\providecommand\testsize{[missing]}
\providecommand\totalsims{[missing]}
\providecommand\windowlength{[missing]}
\providecommand\empiricaltable{[missing]}
\providecommand\empiricaldraws{[missing]}
\providecommand\naivecriticalvalue{[missing]}

\providecommand\phantomsection{}

\author{Gray Calhoun\thanks{Economics Department; Iowa State
    University; Ames, IA 50011.  Telephone: (515) 294-6271.  Email:
    \guillemotleft \protect\url{gcalhoun@iastate.edu}\guillemotright,
    web: \guillemotleft http://gray.clhn.org\guillemotright.
    If you find errors or mistakes in this paper, please email me or
    open a new issue at
    \guillemotleft https://github.com/grayclhn/mixedwindow/issues\guillemotright.
    I'd like to
    thank Helle Bunzel, Todd Clark, Graham Elliott, Yu-Chin Hsu,
    Michael McCracken, Pablo Pincheira, Elie Tamer, Allan Timmermann, Ken West, Stephane
    Meng-Feng Yen, several referees, and participants at the 2011 Midwest Econometrics
    Group meeting and the 2013 \nber-\nsf\ Time Series conference
    for helpful comments and discussions.  I'd also like to thank Amit
    Goyal for providing computer code and data for his 2008
    RFS paper with Ivo Welch \citep{GoW:08}. An earlier version of this paper
    circulated under the name ``An asymptotically normal out-of-sample
  test of equal predictive accuracy for nested models.''}\\%
  Iowa State University}

\title{An asymptotically normal out-of-sample test based on
  mixed estimation windows}

\begin{document}
\maketitle

\addcontentsline{toc}{section}{Abstract}
\begin{abstract}
  \noindent This paper develops a modification of \citepos[\textit{J.
    Econom.}]{ClW:07} adjusted out-of-sample $t$-test. We propose
  using a recursive window to estimate the benchmark model but a
  fixed-length rolling window to estimate the alternative. The
  resulting statistic is asymptotically normal even when the models
  are nested. The
  paper also presents Monte Carlo evidence that this statistic has
  much higher power than existing out-of-sample statistics in a common
  use-case for these tests: when the \dgp\ is subject to instability.
  This procedure is then used to analyze
  \citepos[\textit{Rev. Finan. Stud.}]{GoW:08} excess returns dataset
  and supports their finding that the equity premium is unpredictable
  out-of-sample.

\strut

\noindent Keywords: Forecast Evaluation, Martingale Difference
Sequence, Model Selection, Forecast Encompassing

\strut

\noindent \allcaps{JEL} Classification Numbers: C22, C53

\end{abstract}
\newpage
\markboth{}{}
\tableofcontents
\newpage

\section{Introduction}

This paper proposes an out-of-sample (\oos) test statistic that is
asymptotically normal and correctly centered even when the models
studied are nested. The test is based on one proposed by
\citet{ClW:06,ClW:07}, but we propose estimating the benchmark model
with a recursive window and the alternative model with a fixed length
rolling window. The rolling window ensures asymptotic normality, as in
\citet{GiW:06}, and the recursive window allows the null hypothesis to
be a statement about the specification of the Data Generating Process,
which is the focus of the vast majority of the \oos\ testing
literature.%
\footnote{In particular, this is the focus of \citet{Wes:96},
  \citet{ClM:01}, \citet{Mcc:07}, \citet{ClW:06}, \citet{ClW:07}, and
  many others but not \citet{GiW:06}. See \citet{Wes:06} and
  \citet{ClM:13} for a thorough overview of this literature.} %
This combination of estimation windows also gives our test statistic
high power against alternatives that cause the benchmark model
to be unstable --- structural breaks, time-varying coefficients, or
forms of nonlinearity, for example --- which is a common motivation
for using these tests.

\oos\ tests are common in International Macroeconomics,
Macroeconomics, and Finance (see, for example, \citealt{MeR:83};
\citealt{StW:03}; and \citealt{GoW:08}) and there is a substantial
literature developing the theoretical properties of these statistics,
beginning primarily with \citet{DiM:95} and
\citet{Wes:96}.
In a pair of papers,
\citet{ClW:06,ClW:07} develop an \oos\ test of the null hypothesis
that a small benchmark model is correctly specified.  Their test
compares the forecasting performance of a pair of nested models, and
the null hypothesis is that the innovations in the smaller model form
a Martingale Difference Sequence (\mds).  This test procedure is popular, and
one assumes that this is due in part to the statistic's convenience,
the statistic is approximately normal after adjusting for the
estimation error of the larger model.  Normality comes from a
fixed-length rolling window, as in \citet{GiW:06}, and the adjustment
centers the statistic to have mean-zero under the null.  This statistic is especially
convenient because other \oos\ tests for similar hypotheses
(\citealt{CCS:01}; \citealt{ClM:01,ClM:05}; \citealt{CoS:02,CoS:04};
and \citealt{Mcc:07}; among others) have a nonstandard limit
distribution and place restrictions on the models under consideration,
while other asymptotically normal statistics test a different null
hypothesis \citep{GiW:06} or place assumptions on the models and \dgp\
that are often violated in empirical work (\citealt{DiM:95};
\citealt{Wes:96}; \citealt{WeM:98};
\citealt{Mcc:00}).%
\footnote{\citet{DiM:95} assume that the models are
  not estimated. \citet{Wes:96}, \citet{WeM:98}, and \citet{Mcc:00}
  assume that the models do not converge to the same limit,
  which rules out nesting.} %
However, Clark and West's statistic is only ``approximately normal''
in an informal sense.  Clark and West present Monte Carlo evidence of
the statistic's distribution, but only prove that the statistic is
asymptotically normal with mean zero when the benchmark model is
not estimated \citep{ClW:06}. Estimating the parameters of the smaller
model invalidates their proof.

This paper proposes a modified version of Clark and West's (2006,
2007) statistic and shows that it is
asymptotically normal even when the smaller model is estimated.  To
achieve normality, the pseudotrue benchmark model must be estimated
consistently, but the larger alternative model must continue to be
estimated inconsistently so that the test statistic is not degenerate
when the models are nested. We can meet both needs by
using different window strategies for each model: the benchmark model
is estimated using a recursive window and the alternative with a
fixed-length rolling window.
This approach has the further advantage over existing \oos\ tests for
nested models that the alternative can be essentially arbitrary as
long as high level moment conditions hold. In particular, researchers
can use model selection techniques like the \aic\ or \bic\ to
determine the number of lags to include, the particular exogenous
variables to include, etc. Moreover, although we focus on nested
models in this paper, the approach can be used with non-nested models
as well. As \citet{ClM:11b} have recently argued,
\citepos{Wes:96} results do not hold when the true \dgp\ is nested by
the benchmark and alternative models, which is allowable under the
null hypothesis of interest. (\citealp{ClM:11b}, call this scenario ``overlapping models.'')

The next section presents the intuition and theory for our new
statistic.  Section~\ref{sec:2} presents simulations that compare our
pairwise \oos\ test to \poscw\ original statistics.
Section~\ref{sec:3} demonstrates the use of our statistic by
reanalyzing \citepos{GoW:08} study of excess return predictability and
demonstrates how our results can be used in settings with many
alternative models. Section~\ref{sec:4} concludes. Our results follow
from arguments similar to \citepos{Wes:96} and have been put in a
separate appendix along with some supporting lemmas \citep{Cal:15b}.

@@

\section{Monte Carlo Results}\label{sec:2}
This section presents Monte Carlo experiments demonstrating that
this paper's modified version of \citepos{ClW:07} statistic performs
similarly to their original test in the situations they study, but can
have substantially higher power when the \dgp\ has a structural
break.%
\footnote{All of these simulations were programmed in R
  \citep[version 2.14.0]{R} and use the \allcaps{MASS}
  \citep[7.3-22]{VeR:02} package.} %

The \dgp\ has three different parametrizations: one to study the
tests' size, one to study power under stationarity, and one to study
power if there is a single break in the relationship between the
target and predictors.  The \dgp\ is:
\begin{align*}
  y_{t+1} &= \gamma_{1t} + \gamma_{2t} x_{t} + \ep_{t+1} &
  \gamma_t &=
  \begin{cases}
    (0.5, 0)    & \text{size simulations} \\
    (0.5, 0.35) & \text{power (stable)} \\
    (-0.5, 0)    & t \leq \tfrac{T}{2} \quad \text{power (break)} \\
    (1, 0.35) & t > \tfrac{T}{2} \quad \text{power (break)}
  \end{cases}\\\nonumber
  x_{t+1} &= 0.15 + 0.95 x_{t} + u_{t+1} &
  (\ep_t, u_t)' &\sim iid\ N\Bigg(\begin{pmatrix} 0 \\ 0
  \end{pmatrix}
   , \begin{pmatrix} 18 & -
    0.5 \\ -0.5 & 0.025 \end{pmatrix}\Bigg)
  \\ R &= 120, 240 & P &= 120, 240, 360, 720.
\end{align*}
Both models are estimated by \ols. The benchmark model regresses $y_{t+1}$
on a constant, and the alternative regresses $y_{t+1}$ on a constant and
$x_t$.  \citet{ClW:07} argue that this \dgp\ mimics an asset
pricing application similar to \citepos{GoW:08} which we study in
Section~\ref{sec:3}.

For comparison, we study this paper's new statistic as well as
\poscw\ rolling-window and recursive-window test statistics.  Clark and West
only prove that their rolling-window statistic is asymptotically
normal, and only then if the benchmark model is not estimated, but
their recursive-window statistic is popular in practice and in
simulations tends to perform similarly to their rolling window test.
We use all three of these statistics to test the null that the
benchmark model's innovation is an \mds.%
\footnote{\citet{ClW:07}
  report the performance of the tests proposed by \citet{CCS:01} and
  \citet{ClM:05} as well, and of tests based on the naive Gaussian
  statistic.} %

\begin{table}[tb]
  \centering
  \input{tex/mc1}
  \caption{Size and power of the \oos\ tests in the simulations
    described by Section~\ref{sec:2}, at
    \testsize\% confidence.  These percentages are calculated from \totalsims\
    samples.  Pr[\allcaps{CW} roll.] shows the fraction of simulations for
    which Clark and West's (2007) rolling-window statistic rejects;
    Pr[\allcaps{CW} rec.] shows the fraction of simulations for which
    their recursive-window statistic rejects; and Pr[new] shows the fraction of
    simulations for which this paper's test rejects.}
\label{tab:mc1}
\end{table}

Table~\ref{tab:mc1} presents the simulation results.  For all of the
stable parameter values, the proposed new statistic has similar
rejection probability to \citepos{ClW:07}.  Both of Clark and West's
tests are generally slightly undersized relative to our new test,
which is itself slightly undersized: when $R$ is 120 and $P$ is 360
our test statistic has size 7.6\% and Clark and West's rolling and
recursive window tests have size 7.5\% and 6.2\% respectively, at a
nominal size of 10\%.  For the stable alternative, our new statistic
typically has slightly higher power than Clark and West's rolling
window and lower power than their recursive window.  For example, when
$R$ is 120 and $P$ is 720, the rolling-window test rejects at 66.8\%,
our statistic at 73.0\%, and the recursive window statistic at 82.3\%,
again for a nominal size of 10\%.  In general, the statistics perform
similarly under stability.

For the simulations with a single break, the new statistic has
considerably higher power than \poscw\ original tests across all of
the choices of $R$ and $P$; the rejection probability is more than
twice as large for most parametrizations.  When $R$ is 120 and $P$ is
360 with a nominal size of 10\%, for example, the new statistic
rejects at 96.4\% while the rolling and recursive window statistics
reject at 35.5\% and 32.9\% respectively.  Results for other choices
of nominal size and sample split give similar results.  So mixing
window strategies can give a large power advantage when testing for
time-varying predictability, and performs similarly to the original
test when testing for stable outperformance.

\section{Empirical Illustration}\label{sec:3}

This section demonstrates the use of our new statistic by revisiting
\citepos{GoW:08} study of excess stock returns.  Goyal and Welch argue
that many variables thought to predict excess returns (measured as the
difference between the yearly log return of the S\&P 500 index and the
T-bill interest rate) on the basis of in-sample evidence fail to do so
out-of-sample.  To show this, Goyal and Welch look at the forecasting
performance of models using a lag of the variable of interest, and
show that these models do not significantly outperform the excess
return's recursive sample mean.

Here, we conduct the same analysis, but using this paper's \mds\ test.
The benchmark model is the excess return's sample mean (as in the
original) and the alternative models are of the form
\begin{equation*}
  \mathit{excess~return}_{t+1} = \beta_{0} + \beta_{1}\
  \mathit{predictor}_{t} + \ep_{t+1},
\end{equation*}
where $\beta_{0}$ and
$\beta_{1}$ are estimated by \ols\ using a \windowlength-year window.
The predictors used are listed in the \emph{predictor} column of
Table~\ref{tab:em1}. \citep[See][for a detailed description of the
variables.]{GoW:08}  We also consider \citepos{CaT:08} proposed
correction to the models, that the forecasts be bounded below by zero
since negative forecasts are incredible, as well as two simple
combination forecasts, the mean and the median (over both the original
and the non-negative forecasts).  The data set is annual data
beginning in 1927 and ending in 2009, and the rolling window uses
\windowlength\ observations.%
\footnote{This statistical analysis was conducted in R \citep{R} and
  uses the MASS \citep[7.3-22]{VeR:02} package.} %

\begin{table}[tb!]
  \centering
  \empiricaltable
\caption{Results from \oos\ comparison of equity premium prediction
  models; the benchmark is the recursive sample mean of the equity
  premium and each alternative model is a constant and single lag of
  the variable listed in the \emph{predictor} column.  The dataset begins
  in 1927 and ends in 2009 and is annual data. The \emph{value} column
  lists the value of this paper's \oos\ statistic, the \emph{naive}
  column indicates whether the statistic is significant at standard
  critical values, and the \emph{corrected} column indicates significance
  using critical values that
  account for the number of models.  See Section~\ref{sec:3} for details.}
\label{tab:em1}
\end{table}

Table~\ref{tab:em1} presents the results for each model.  The column
\emph{value} gives the value of the test statistic for each model,
while \emph{naive} indicates whether the statistic is greater than the
standard 10\% critical value (\naivecriticalvalue). Three predictors
are significant at the naive critical values for both the original and
bounded forecasts: the dividend yield, long term interest rate, and
book to market ratio, and the median forecast is significant as well.
This could suggest that excess returns are not an \mds\ and that
information in these three variables is useful for predicting returns.

However, we know that this is an extremely optimistic assessment of
the models' performance. We are conducting \nmod\ simultaneous
hypothesis tests, so it is likely that some will reject by chance.
There are several approaches that could accommodate this multiplicity and a full
treatment is beyond the scope of this paper, however, it is
straightforward to use our results to
derive a valid critical value similar to~\citet{Whi:00}.

Let $\fb_i$ be the \oos\ statistic associated with the $i$th alternative
forecast, $\yh_{i,t+1}$. The arguments underlying our results apply essentially unchanged to
multivariate $f_t$, so the continuous mapping theorem implies that
\begin{equation*}
  \max_{i=1,\dots,\nmod} \sqrt{P} \fb_i/\sigmah_{2i} \to^d \max_{i=1,\dots,\nmod} W_i,
\end{equation*}
where $W \sim N(0, V)$ and $V$ is the $\nmod
\times \nmod$ correlation matrix with elements
\begin{equation*}
  V_{ij} = \lim \frac{\cov(\fb_i, \fb_j)}{\var(\fb_i)^{1/2} \var(\fb_j)^{1/2}}.
\end{equation*}

To estimate $V$, we use the correlation matrix associated with the
multivariate analogue of $\sigmah_2$,
\[
\oavg{t}\Big[(\fh_t - \fb)(\fh_t - \fb)' + (\fh_t - \fb)(\gh_t - \gb)'
+ (\gh_t - \gb)(\fh_t - \fb)' + 2 (\gh_t - \gb)(\gh_t - \gb)' \Big]
\]
where $\fh_t$ and $\gh_t$ are vectors with $i$th elements
\begin{gather*}
  \fh_{it} = (y_{t+1} - x_t'\bh_t)^2 - (y_{t+1} - \yh_{i,t+1})^2 + (x_t'\bh_t - \yh_{i,t+1})^2
  \intertext{and}
  \gh_{it} = 2\, \Bigg[\oavg{s} (x_s'\bh_s - \yh_{i,s+1}) x_s'\Bigg]\,
            \Bigg[\tfrac{1}{T-1} \sum_{s=1}^{T-1} x_s x_s'\Bigg]^{-1} x_t \eph_{t+1}
\end{gather*}
respectively. Call this estimate $\hat V$ and let $\hat c$ denote the
$0.90$ quantile of the distribution of $\max_i \hat W_i$, with
$\hat W \sim N(0, \hat V)$.  Then
\begin{equation*}
  \limsup_{T \to \infty} \Pr\Big[\max_{i=1,\dots,\nmod} \sqrt{P} \fb_i / \sigmah_{2i} > \hat c\Big] \leq 0.10,
\end{equation*}
under the null hypothesis that excess returns are an \mds\ with
respect to all of the information contained in the variables listed in
Table~\ref{tab:em1}, making $\hat c$ an asymptotically valid critical
value.%
\footnote{\citet{Han:05} makes the point that multiple one-sided
  comparisons can have poor power if irrelevant predictors are
  included in these tests and proposes a threshold for discarding very
  poor forecasts. His threshold is well below our worst performing
  model, so this issue is not a concern here.} %

We calculate $\hat c$ by generating \empiricaldraws\ draws from
$N(0,\hat V)$, giving a value of \empiricalcriticalvalue, and the
\emph{corrected} column of Table~\ref{tab:em1} denotes the models that
remain significant at 10\% with this critical value. Using this
critical value, none of the predictors are significant, which
gives additional support to \citepos{GoW:08} conclusion that excess
returns are unpredictable and also demonstrates the importance of
correcting for multiplicity in these studies.

\section{Discussion}\label{sec:4}
This paper presents an \oos\ test statistic similar to \poscw\ that is
asymptotically normal when comparing nested or non-nested models.
Normality is achieved by estimating the alternative model using a
fixed-length rolling window --- as do Clark and West --- but
estimating the benchmark model with a recursive window.  Simulations
indicate that the new statistic behaves similarly to Clark and West's
original test when the \dgp\ is stable but can have much higher power
when the \dgp\ has structural breaks. We also have presented an
empirical study of the equity premium that demonstrates how to use
these results with several alternative models.

\newpage
\phantomsection
\addcontentsline{toc}{section}{References}
\bibliography{texextra/references}

\newpage
\appendix
\section{Supplemental appendix (not for publication)}
\newcommand{\WesA}[1][]{\ocltb{t}
  (F_t^{#1} - F) B^{#1} H_t^{#1}}
\newcommand{\WesB}[1][]{\ocltb{t} F (B_t^{#1} -
  B^{#1}) H_t^{#1}}
\newcommand{\WesC}[1][]{\ocltb{t}
  (F_t^{#1} - F) (B_t^{#1} - B^{#1}) H_t^{#1}}

This appendix contains mathematical proofs and some supporting Lemmas
for the paper, ``An asymptotically normal out-of-sample test based on
mixed estimation windows'' \citep{Cal:15}. Define the following
additional terms:
\begin{equation*}
  F_t(\beta) = 2 (2 x_t'\beta - \yh_{t+1} - y_{t+1}) x_t',
\end{equation*}
$F_t = F_t(\btrue)$, $\Fh_t = F_t(\bh_t)$, $F = \E F_t$, $B = (\E x_t
x_t')^{-1}$, $B_t = (\sum_{s=1}^{t-1} x_s x_s' / (t-1))^{-1}$, and
$H_t = \sum_{s=1}^{t-1} x_s \ep_{s+1} / (t-1)$.
And let $\lVert \cdot \rVert$ denote the $L_2$ norm in $\Re^k$.
Note that Assumptions~\ref{a1} and~\ref{a3} imply that $f_t$, $g_t$,
and $F_t$ are all strong mixing of size $-r/(r-2)$ or uniform mixing
of size $-r/(2r-2)$ and are stationary with bounded $r$th moments.

\subsection{Proof of Theorem \ref{res:1}}
  Let $R'$ be a new sequence such that $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$, and then rewrite the centered \oos\ average as
  \begin{equation}\label{eq:6}
    \sqrt{P} (\fb - \E \fb^*)
    = \ocltb{t} (\fh_t - \E f_t)
      + \tfrac{1}{\sqrt{P}} \osumc{t} (\fh_t - \E f_t).
  \end{equation}
  Lemma~\ref{res:a1} ensures that the second summation is $o_p(1)$, so
  we can rewrite~\eqref{eq:6} as
  \begin{align*}
    \sqrt{P} (\fb - \E \fb^*)
    &= \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \\
    & \quad + \WesA + \WesB \\ & \quad + \WesC + \oclt{t} w_t + o_p(1)
  \end{align*}
  where $w_t$ equals $2 (\bh_t - \btrue)' x_t x_t' (\bh_t - \btrue)$.
  Lemma~\ref{res:a4} shows that
  \begin{gather}
    \WesA \to^{p} 0 \label{eq:11} \\
    \WesB \to^{p} 0 \label{eq:12} \\
    \intertext{and}
    \WesC \to^{p} 0 \label{eq:13}
  \end{gather}
  and Lemma~\ref{res:a2} along with the \clt\ ensures that $\oclt{t}
  w_t = o_{p}(1)$. The proof that
  \begin{equation*}
    \ocltb{t} (f_t - \E f_t) + F B \ocltb{t} H_t \to N(0, \sigma^2).
  \end{equation*}
  follows the same argument as in \citet{Wes:96} and \citet{Mcc:00}.

\subsection{Proof of Lemma~\ref{lem:2}}

We will only prove $\sigmah_2 \to^p \sigma$. The result for
$\sigmah_1$ is essentially the same and uses \citepos{JoD:00} Theorem
2.1 for the \hac\ equivalent of Equations~\eqref{eq:1}--\eqref{eq:7}.

  First, we can rewrite the components of the variance estimator as
  \begin{align*}
    \sh_{21} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]^2 \\
    \sh_{22} &= \oavg{t} \Big[(f_t - \E f_t) + (\fh_t - f_t) - (\fb - \E f_t)\Big]
                        \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb - \E g_t)\Big]
    \intertext{and}
    \sh_{23} &= \oavg{t} \Big[(g_t - \E g_t) + (\gh_t - g_t) - (\gb + \E g_t)\Big]^2
  \end{align*}
  so $\sigmah_2 \to^p \sigma$ as long as the following hold:
  $\fb - \E \fb^* \to^p 0$,
  $\gb - \E \gb^* \to^p 0$,
  \begin{gather}
    \oavg{t} (f_t - \E f_t)^2 \to^p \lim \var(\sqrt{P} \fb^*) \label{eq:1} \\
    \oavg{t} (g_t - \E g_t)^2 \to^p \lim \var(\sqrt{P} \gb^*) \label{eq:3} \\
    \oavg{t} (f_t - \E f_t) (g_t - \E g_t) \to^p \lim \cov(\sqrt{P} \fb^*, \sqrt{P} \gb^*) \label{eq:7} \\
    \oavg{t} (\fh_t - f_t)^2 \to^p 0, \label{eq:4}
    \intertext{and}
    \oavg{t} (\gh_t - g_t)^2 \to^p 0. \label{eq:5}
  \end{gather}
  The first two results are implied by the proof of
  Theorem~\ref{res:1} and~\eqref{eq:1}, \eqref{eq:3}, and~\eqref{eq:7}
  follow from the \lln, since each summand is an $L_1$-mixingale of
  size $-1$ \citep[see, for example][Theorem 17.5]{Dav:94}, so it suffices to
  prove~\eqref{eq:4} and~\eqref{eq:5}.

  As in the proof of Theorem~\ref{res:1}, let $R'$ be a new sequence such that $R' \to \infty$ as
  $T \to \infty$ and $R' = o(\sqrt{P})$.  Straightforward algebra reveals
  that~\eqref{eq:4} holds if
  \begin{gather}
    \oavg{t} ((\bh_t - \btrue)' x_t)^4 \to^p 0 \label{eq:10}
    \intertext{and}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \to^p 0.\label{eq:14}
  \end{gather}
  The \allcaps{LHS} of~\eqref{eq:10} is bounded by
  \begin{align*}
    \oavg{t} &\|\bh_t - \btrue\|^4 \|x_t\|^4\\
    &= \oavgc{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 + \oavgb{t} \|\bh_t - \btrue\|^4 \|x_t\|^4 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^4 \,  \oavgc{t} \|x_t\|^4 + \omaxb{t} \|\bh_t - \btrue\|^4 \,  \oavgb{t} \|x_t\|^4 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  by Lemma~\ref{res:a2} and the \lln.
  A similar argument holds for the second term:
  \begin{align*}
    \oavg{t} (x_t'(\bh_t - \btrue))^2 &(2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &= \oavgc{t} (x_t'(\bh_t - \btrue))^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\quad+ \oavgb{t} \big(x_t'(\bh_t - \btrue)\big)^2 (2 x_t'\btrue - y_{t+1} - \yh_{t+1})^2 \\
    &\leq \omaxc{t} \|\bh_t - \btrue\|^2 \oavgc{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &\quad+ \omaxb{t} \|\bh_t - \btrue\|^2 \oavgb{t} \|x_t (2 x_t'\btrue - y_{t+1} - \yh_{t+1})\|^2 \\
    &= O_p(R'/P) + o_p(1)
  \end{align*}
  again by Lemma~\ref{res:a2} and the \lln. Both terms converge to
  zero in probability by construction. The proof of~\eqref{eq:5} is similar.

\subsection{Supporting results}

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a1}}
\begin{alem}\label{res:a1}
  Suppose the conditions of Theorem~\ref{res:1} hold, and define $R'$
  to be a sequence that satisfies $R' \to \infty$ as $T \to \infty$
  and $R' = o(\sqrt{P})$. Then
  \begin{equation*}
    \ocltc{t} (\fh_t - \E f_t) \to^p 0.
  \end{equation*}
\end{alem}

\begin{proof}
  We can rewrite this summation as
  \begin{multline*}
    \ocltc{t} (\fh_t - \E f_t) = \ocltc{t} (f_t - \E f_t) + \\
    \ocltc{t} (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue)
    + \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2.
  \end{multline*}
  Each of these individual summations can be shown to converge to
  zero in probability. First,
  \begin{equation*}
    \E \Big\lvert \ocltc{t} (f_t - \E f_t) \Big\rvert
    \leq \ocltc{t} \E\lvert f_t - \E f_t \rvert
    = O(R'/\sqrt{P}).
  \end{equation*}
  Also,
  \begin{align*}
    \Big\lvert \ocltc{t} & (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t'(\bh_t - \btrue) \Big\rvert \\
    &\leq \ocltc{t} \big\lVert (4 x_t'\btrue - 2 y_{t+1} - 2 \yh_{i,t+1}) x_t \big\rVert
    \omaxc{t} \lVert  \bh_t - \btrue \rVert \\
    & = O_p(R'/\sqrt{P})
  \end{align*}
  and
  \begin{equation*}
    \Big\lvert \ocltc{t} (x_t'\bh_t - x_t'\btrue)^2 \Big\rvert
    \leq \ocltc{t} \lVert x_t \rVert^2 \omaxc{t} \lVert \bh_t - \btrue \rVert^2
    = O_p(R'/\sqrt{P}).
  \end{equation*}
  by Lemma~\ref{res:a2} and the \lln. Since $R'/\sqrt{P} \to 0$ by
  construction, this completes the proof.
\end{proof}

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a2}}
\begin{alem}\label{res:a2}
  Suppose $a \in [0,1/2)$ and Assumptions~\ref{a1}~--~\ref{a4}
  hold, and let $R'$ be a sequence such that $R' \to \infty$ as $T \to
  \infty$ and $R' = o(\sqrt{P})$. Then
  \begin{enumerate}
  \item $\omaxb{t} | (t-1)^a H_t | \to^p 0$,
  \item $\omaxc{t} | (t-1)^a H_t | = O_p(1)$,
  \item $\omaxb{t} | B_t - B | \to^p 0$,
  \item $\omaxc{t} | B_t - B | = O_p(1)$,
  \item $\omaxb{t} | (t-1)^a(\bh_t - \btrue) | \to^{p} 0$, and
  \item $\omaxc{t} | (t-1)^a(\bh_t - \btrue) | = O_p(1)$,
  \end{enumerate}
  where the absolute value is taken as the largest of the
  element-by-element absolute values.
\end{alem}

\noindent%
To streamline the
presentation, we'll assume in these proofs that $x_t$ is a scalar.
\begin{proof}
  We will prove each part in order.
  \begin{enumerate}
  \item Our assumptions ensure that $x_t \ep_{t+1}$ is $L_2$-mixingale
    of size $-1/2$ \citep[see Theorem 17.5 of][]{Dav:94}; let $c_t$
    and $\zeta_k$ denote its mixingale
    constants and coefficients. Note that, for any $b$, $t^{b} x_t \ep_{t+1}$ is
    also an $L_2$-mixingale array with constants $t^{b} c_s$ and
    coefficients $\zeta_k$, since
    \begin{align*}
      \| \E_{t-k} t^{b} x_t \ep_{t+1} \| &= t^{b} \| \E_{t-k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_k
    \end{align*}
    and
    \begin{align*}
      \| t^{b} x_t \ep_{t+1} - t^{b} \E_{t+k} x_t \ep_{t+1} \| &= t^{b} \|  x_t \ep_{t+1} - \E_{t+k} x_t \ep_{t+1} \| \\
      &\leq (t^{b} c_t) \zeta_{k+1}.
    \end{align*}

    Let $\delta$ be a positive number less than $1/2 - \alpha$, so
    \begin{align*}
      \E\Bigg[\omaxb{t} \Big|(t-1)^{a-1} & \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} \E\Bigg[\omaxb{t} \Big| \sum_{s=1}^{t-1} x_s \ep_{s+1} (s-1)^{a-1+\delta} \Big|^2\Bigg] \\
      &\leq (R'-1)^{-2\delta} O(1) \sum_{s=1}^{T-1} (s-1)^{2(a - 1 + \delta)}
    \end{align*}
    where the second inequality follows from \citepos{Mcl:75} maximal
    inequality (also available as \citealp{Dav:94}, Theorem 16.9 and
    Corollary 16.10). The summation converges to a constant and
    $(R'-1)^{-2\delta} \to 0$ as $T \to \infty$, completing the proof.

  \item Now $t^{a-1} x_t \ep_{t+1}$ is an $L_2$-mixingale of size
    $-1/2$ and we can again use \citepos{Mcl:75} maximal inequality to get
    \begin{align*}
      \E \Big\lvert \omaxc{t} \Big((t-1)^{a - 1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big)^2 \Big\rvert
      &\leq \E \Big\lvert \omax{t} \Big(\sum_{s=1}^{t-1} s^{a-1} x_s \ep_{s+1} \Big)^2 \Big\rvert \\
      &= O(1) \sum_{s=1}^{R'-1} s^{2a - 2}
    \end{align*}
    which converges to a finite limit.
  \item The same argument used in Part 1 implies that $\omaxb{t} |
    B_t^{-1} - B^{-1}| \to^p 0$. Since matrix inversion is continuous,
    the result follows.
  \item Holds by Assumptions~\ref{a1} and~\ref{a3}.
  \item We have
    \begin{align*}
      \omaxb{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      &\leq \omaxb{t} |\hat{B}_t - B|
      \omaxb{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxb{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|
    \end{align*}
    and both terms converge to zero in probability by Parts 1 and 3.
  \item Similar to the previous argument, we have
    \begin{align*}
      \omaxc{t} | (t-1)^a (\hat{\beta}_t - \btrue) |
      & \leq \omaxc{t} | \hat{B}_t - B | \omaxc{t} \Big|(t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big| \\
      &\quad + \omaxc{t} \Big| B (t-1)^{a-1} \sum_{s=1}^{t-1} x_s \ep_{s+1} \Big|.
    \end{align*}
    Both terms are $O_p(1)$ by Parts 2 and 4. \qedhere
  \end{enumerate}
\end{proof}

\phantomsection
\addcontentsline{toc}{subsubsection}{Lemma \ref{res:a4}}
\begin{alem}\label{res:a4}
  Under the conditions of Theorem~\ref{res:1}, Equations
  \eqref{eq:11}--\eqref{eq:13} hold.
\end{alem}

>>>>

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "mixedwindow"
%%% TeX-command-extra-options: "-shell-escape"
%%% End:
